### 2021-04-10 Submission template.Rmd
Template updated with a plan

### Introduction

>>>>

### Plan

* Write introduction: About Covid, about anxiety, about how 19-28 more(no more?) prone to it. Write that our analysis shows that a lot of 18-29 are in the college.

* Write introduction: calculate (using historical data) how many 18-29 is in college. Maybe prediction for 2020. 
* Describe data sources used in this research:
   - Anxiety
   - Covid
   - Google

* Overview trends in anxiety data (functional analysis)

* Panel modelling

* Discussion/results.
